#STRINGR


```{r}
install.packages("stringr")
library(stringr)
```

To know the length of the string. nchar() of base R package gives the same output.
```{r}
char<-"How are you?"
str_length(char)
```

To select a particular position in the string. Here 3 is the starting postion and 5 is the end position 

```{r}
str_sub(char, 3,5)
```

You can also assign a value to particualr position in a string

```{r}
str_sub(char,1,3) <- "Who"
char
```

You can also duplicate a string

```{r}
str_dup(char,2)
```

You can add whitespaces to a string

```{r}
char1 <- "Hi"
str_pad(char1,10)
str_pad(char1,10,"both")
```

You can also remove the whitespaces

```{r}
char3 <- "   How   "
str_trim(char3)
str_trim(char3,side="left")
```

For creating a matrix of strings

```{r}
char5 <- str_c("How are you","I'm good","Where are you","I'm from united states of america, and its a good country")
char5
```

For wrapping text

```{r}
str_wrap(char5,width=40)
```

Upper, lower and title

```{r}
char6 <- "What is your name?"
str_to_upper(char6)
str_to_lower(char6)
str_to_title(char6)

```

```{r}
char7<-c("a","z","u","f")
str_order(char7)
str_sort(char7)
```

```{r}
strings <- c(
  "apple", 
  "219 733 8965", 
  "329-293-8753", 
  "Work: 579-499-7527; Home: 543.355.3679"
)
phone <- "([2-9][0-9]{2})[- .]([0-9]{3})[- .]([0-9]{4})"

str_detect(strings,pattern=phone)
```

```{r}
str_replace_all(strings, phone, "XXX-XXX-XXXX")
```

```{r}
str_split(strings[1], "", n=3)
```

```{r}
install.packages("reshape2")
```

```{r}
require(reshape2)
library(dplyr)
x = data.frame(subject = c("John", "Mary"), 
               time = c(1,1),
               age = c(33,NA),
               weight = c(90, NA),
               height = c(2,2))
x
molten = melt(x, id = c("subject", "time"))
molten
group = group_by(molten,subject,variable)
group
```

```{r}
grocery <- data.frame(c("t1","t2","t3","t4","t5"), c('Bread,jelly,butter','bread,butter','bread,milk,butter','beer,bread','beer,milk'))
colnames(grocery)=c("transaction","Items")
grocery
```


